\textbf{INSERT TITLE HERE}

### 2013-11-16 LaTeX/paper.tex
added a def

\subsection{Part 1?}

\subsection{Part 2?}

>>>>

\subsection{Part 1?}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.

\subsection{Ambulance Distributor}
Once the zone-to-zone coverages have been
